% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode

\documentclass[12pt]{report}
\usepackage[utf8]{inputenc}

% Set the geometry early as other packages might depend on it for page/line width etc.
\usepackage[a4paper]{geometry}

% Force usage of Arial for the entire document
\usepackage[scale=1.0]{newtxtext}

\usepackage{graphicx}

\usepackage[parfill]{parskip} % Begin paragraphs with an empty line rather than an indent

% Global Packsges
\usepackage{booktabs} % for much better looking tables
\usepackage{tabularx}
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
\usepackage[hidelinks]{hyperref}

%%% HEADERS & FOOTERS
\usepackage{fancyhdr} % This should be set AFTER setting up the page geometry
\pagestyle{fancy} % options: empty , plain , fancy
\renewcommand{\headrulewidth}{0pt} % customise the layout...
\lhead{}\chead{}\rhead{}
\lfoot{}\cfoot{\thepage}\rfoot{}

\title{World in Conflicts\\\normalsize{Rev 1.0}}
\author{Stefano Fam\`a}
\date{2024.08.25}

\begin{document}
\maketitle
\tableofcontents
\newpage

\chapter{Preamble}
\section{Project Description}

\chapter{Player Interaction}
\section{Camera}
\begin{itemize}
\item Bird-Eye View.
\item User can rotate only along the Z-axis.
\item User can traslate the camera along all axes.
\item Blocked by:
	\begin{itemize}
	\item Terrain.
	\item Water.
	\item Buildings.
	\item Edges of the map.
	\item Maximum altitude.
	\end{itemize}
\item Any non-blocking entities that collide with the camera will become transparent with a design-modifiable alpha value.
\end{itemize}

\chapter{AI}
\section{Unit Controller}
\begin{enumerate}
\item Receives input from Player or Mastermind Controller.
\item Inputs are Actions, that are decoded into smaller tasks.
\item Outputs are events that are sent to the Player or Mastermind Controller.
\end{enumerate}

List of outputs:

\begin{tabularx}{\linewidth}{p{3cm} X p{3cm}}
\toprule
\textbf{Output} & \textbf{Trigger} & \textbf{Data Sent}\\ \midrule
Enemy Spotted   & Whenever an enemy that was hidden, appears. & Spotted AActor.\\ \midrule
Suffered Damage & Got hit by an unkown attacker (like artillery, or hidden enemy). & Self.\\ \midrule
Got Attacked    & Got hit and I know who is. & Attacker AActor.\\ \midrule
Less Than \% HP & Design-configurable list of percentages that when the
                  HP is below that, will send the event.
                  In case of multiple thresholds being triggered in the same frame,
                  only the smallest will be sent. & Self.\\ \midrule
Dead            & When the unit dies.             & Self and Killer AActor (if present).\\ \midrule
Killed Enemy    & When this unit kills another one. & Self and Killed AActor.\\
\bottomrule
\end{tabularx}

\section{Mastermind Controller}
\begin{enumerate}
\item Long/Mid/Short-term Plans.
\item Real Military Strategies.
\item Decisions go from Top to Bottom, while Reactions go from Bottom to Top.
\item Recieves inputs from Unit Controller's Outputs.
\item Long-term Plans:
	\begin{enumerate}
	\item Win the battle
	\item Defend Allies
	\item Support Allies
	\end{enumerate}
\item Mid-term Plans:
	\begin{enumerate}
	\item Define goals that are required to accomplish the Long-term ones
	\item Capture Control points, defend them, stall enemy, reinforce ally, transport troops etc.
	\end{enumerate}
\item Short-term Plans:
	\begin{enumerate}
	\item Define goals that are required to accomplish the Short-term ones, and make the AI more reactive and life-like.
	\item Those are the only ones that are actual Actions sent to the various Unit Controllers.
	\end{enumerate}
\end{enumerate}

\end{document}
